---
title: "Hotel Bookings Using Factors"
output: html_document
---

<br>
 
This exercise gives practice manipulating factors in R, using the
`forcats` package.

We'll be using the same `hotels` dataset as previously.

```{r load-pkg, message = FALSE}
library(tidyverse)
library(skimr)
```

```{r load-data, message = FALSE}
hotels <- read_csv('data/hotels.csv')
```

<br>


First, knit this document and view the following visualization. 

```{r plot, fig.width=10}
hotels %>%
  group_by(hotel, arrival_date_month) %>%                # group by hotel type and arrival month
  summarize(mean_adr = mean(adr), .groups = "keep") %>%  # calculate mean adr for each group
  ggplot(aes(
    x = arrival_date_month,                              # x-axis = arrival_date_month
    y = mean_adr,                                        # y-axis = mean_adr calculated above
    group = hotel,                                       # group lines by hotel type
    color = hotel)                                       # and color by hotel type
    ) +
  geom_line() +                                          # use lines to represent data
  theme_minimal() +                                      # use a minimal theme
  labs(x = "Arrival month",                              # customize labels
       y = "Mean ADR (average daily rate)",
       title = "Comparison of resort and city hotel prices across months",
       subtitle = "Resort hotel prices soar in the summer while ciry hotel prices remain relatively constant throughout the year",
       color = "Hotel type")
```

<br>



1. How are the months ordered? What would be a better order?

1. Reorder the months on the x-axis (levels of `arrival_date_month`) in a
way that makes more sense. You will want to use a function from the
**forcats** package, see the
<a href="https://forcats.tidyverse.org/reference/index.html" target="_blank" style="color: blue">forcats package</a>
for documentation.

1. Next, change the y-axis label so the values are shown with dollar
   signs, e.g. $80 instead of 80. You will want to use a function from
   the **scales** package, see the
   <a href="https://scales.r-lib.org/reference/index.html" target="_blank" style="color: blue">scales
   package</a>
   for documentation.  You will also need to use the <a 
   href="https://ggplot2.tidyverse.org/reference/scale_continuous.html" target="_blank" style="color:
   blue">scale_y_continuous</a> function.  Look carefully through the <a
   href="https://ggplot2-book.org/scales-position" target="_blank" style="color: blue">examples</a> here.



<br>


<br>


<br>


<br>


<br>


<br>


<br>


<br>


<br>


<br>

